Algorithm explanation

### 2013-08-28 article/horn.tex
Conclusion
Formatting for final

Consider these two ways of transformation, we show a pseudo-code for
\transGraph~procedure.  The procedure is given the graph $G$, the
predicate templateset $T$, and the unsatisfiable core
$\mathcal{U}$. It returns the transformed graph $G'$ and the new
templateset $T'$.

@@

% TODO: What's this paragraph?
traverses the input graph in the topological order on $V_\Rightarrow$,
and concatenate the constraints from predecessors to build the problem
constraints.  Each process to build a constraint on $\mathcal{HC}_v$
for all vertices $v \in V_\Rightarrow$ is equivalent to generate a
linear constraint in interpolation.

>>>>

Consider these two ways of transformation, we show a pseudo-code for
\linebreak \transGraph~procedure.  The procedure is given the graph
$G$, the predicate templateset $T$, and the unsatisfiable core
$\mathcal{U}$. It returns the transformed graph $G'$ and the new
templateset $T'$.

@@

### 2013-08-28 article/thesis.tex
Include graphics
Formatting for final

\jtitle{Lipsum}
\jauthor{Lipsum}
\jsupervisor{Lipsum}

@@

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{stmaryrd}
\usepackage{syntax}
\usepackage{url}

@@

\input{eabstract.tex}
\begin{jabstract}
Lorem ipsum dolor sit amet, consectetur adipiscing elit.  Morbi
vulputate ornare arcu et malesuada.  Proin sem urna, feugiat et velit
ac, elementum blandit orci.  Etiam ut neque ac felis laoreet venenatis
eget quis enim.  Ut aliquam dapibus sem egestas molestie.  Ut sit amet
porttitor orci, id fermentum dui.  In non dui at ante sagittis
malesuada at in neque.  Fusce euismod velit quis ante ullamcorper
qsodales.
\end{jabstract}
\maketitle

>>>>

\jtitle{プログラム検証のための非循環 Horn 節充足問題における小さな解の生成}
\jauthor{竹井 悠人}
\jsupervisor{小林 直樹}

@@

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage[dvipdfmx]{graphicx}
\usepackage{listings}
\usepackage{stmaryrd}
\usepackage{syntax}
\usepackage{url}

@@

\input{eabstract.tex}
\input{jabstract.tex}
\maketitle
